\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}A Little Bit All Over The Place& {\color{purple} \faPizzaSlice }\end{tblr}\vspace{-1em}}

Soup soup!!! We bring great food and well, whatever else we can muster up really. Smoked cookies, a table of stamps, paints and colored pencils, wire wrapping, jam sessions, and whatever else we manage to think of. At the end of the day we really are just A Little Bit All Over The Place.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}ADA/SHUTTLE HQ& {\color{purple} }\end{tblr}\vspace{-1em}}

Ada/shuttle hq



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Abiding Grove& {\color{purple} \faIcon{glass-martini-alt} \faUmbrellaBeach \faDice }\end{tblr}\vspace{-1em}}

Abiding Grove -- Dudeism Camp\n\nStep into a laid-back sanctuary of play, story, and connection. Abiding Grove channels the spirit of Dudeism with a welcoming lounge atmosphere where burners can gather, unwind, and engage.\n\nMornings feature our Conspiracay Coffee Bar serving coffee and tea to ease into the day. As the sun sets, the space transforms into an open-air cinema with Lebowski-inspired films, paired with snacks and White Russians.\n\nThroughout the day, enjoy a variety of interactive games including Disc-O-Golf, bocce, Magic Stones, Truth-or-Dare Jenga, and classic dice and card games. Relax in our hammock-filled lounge and stay awhile.\n\nAbide, play, and connect.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Acid Communism& {\color{purple} \faChild \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

What if default world didn't exist? Join us in imagining a world where exploitative capitalism is not the only possible reality. We've got free food, interactive art, and community where we're building a world where the burn can live everywhere. We are the original home of the Nail Polish Glory Hole! --- insert your boring hand in the hole and get a glorious nail polish surprise! We also host the Sparkle Pony Express, where you can write letters to burners and deliver them by pony.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Ad Fontes& {\color{purple} \faMusic }\end{tblr}\vspace{-1em}}

Vinyl Driven Twisted Disco



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Adventures Beyond& {\color{purple} \faUserAstronaut }\end{tblr}\vspace{-1em}}

A camp centered around whimsy and fun through TTRPG systems like D\\&D and VTM, as well as some light foam sword fighting lessons during the day.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Ah-Mazing!& {\color{purple} \faChild \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Stop by and play our maze wall ball game and other carnival-style games!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Astro-nots& {\color{purple} }\end{tblr}\vspace{-1em}}

Where bad science makes great sense and the truth is actively avoided. We are the premier destination for reverse pioneers, certified tin foil engineers and amateur monster hunters. Our mission is to explore the deep cosmos, hidden forests and bottomless lakes using zero peer-reviewed data and 100\% unadulterated imagination.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Bacchanalia& {\color{purple} \faPizzaSlice }\end{tblr}\vspace{-1em}}

Makers of mischief, rowdy revelers.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Banana Hammocks& {\color{purple} \faIcon{glass-martini-alt} \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

You know us at Love Burn, you've enjoyed us at BRC now it's time to go TO THE MOON! Bananas, Hammocks and fun shenanigans!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Bark Park& {\color{purple} \faUserAstronaut \faChild \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Welcome to Camp Bark Park! A group of fun loving pups each on our own journey to share and explore the plethora of experiences at To The Moon! Stop by and rest your paws a bit in our large comfortable shade structure on your way to your next adventure!  Come share some wags at Camp Bark Park! DONT MISS OUT ON SATURDAY MORNING PANCAKES!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Bear Necessities& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

A chill space to escape the heat and hydrate! We have ALL the Bear Necessities 🐻



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Big Fluffy Cloud& {\color{purple} \faChild \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

The fluff that needs to be seen to be believed.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Big Spooky Energy& {\color{purple} }\end{tblr}\vspace{-1em}}

Come join us for all things spooky! We have some carnival style games, a spooky chill space, and a full walk through haunted house. Whatever level of spooky youre into, we've got something for you!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Bingopalooza& {\color{purple} }\end{tblr}\vspace{-1em}}

BINGOPALOOZA is invading CENTER CAMP.\n\n\emoji{fire}🎱\emoji{fire}🎱\emoji{fire}\emoji{fire}🎱\emoji{fire}🎱\emoji{fire}\emoji{fire}\n\nWe are bringing you a low budget production but high energy bingo with incredible gifts to win! We've got silly and oh shit I didn't know I needed that gifts!\n\nThe only thing you need to bring is yourself and watch us professionally handle the balls! 😉\n\nIt's not polished. It's not sponsored. It is aggressively joyful.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}CAMP NOT YOUR MOM& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

camp home from home but I'm not your mom we are a ranger support camp for the loves that wonder so we can spacewalk safely also come take a picture with a pair of wings will have to where anyone can take a photo with this amazing tapestry



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Cameo’s Closet& {\color{purple} \faChild }\end{tblr}\vspace{-1em}}

A clothing exchange with a boutique experience, offering glamorous garments, two fitting rooms, and a vanity drawer full of goodies like body glitter, temporary tattoos, and more!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Camp Camp& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Making our To The Moon Debut. Here to provide a fun comfortable cuddle space to hang out and recharge. Maybe some spontaneous yoga classes and dance workshops.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Camp Pretty Lights& {\color{purple} \faUserAstronaut \faMusic }\end{tblr}\vspace{-1em}}

Come, be dazzled by our Pretty Lights and Shadowbox with friends both new and old. We are an original all-purpose hippie trap and beacon of luminescence. Join us for Metal Hour on Friday @ 4pm



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Camp Procrastination& {\color{purple} }\end{tblr}\vspace{-1em}}

We were going to write a cool-sounding description but got busy... it's on our to-do list, really... But you can come by any time and absolve yourself of your *own* procrastination! Write down things you've been putting off onto one of our blank ``to-do'' lists. We'll burn these in the temple burn... or maybe the next weekend in our backyard... depends on when we get around to it... to help give energy to the things you want to accomplish.  :)



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Cool as Fuck!& {\color{purple} \faIcon{glass-martini-alt} }\end{tblr}\vspace{-1em}}

We are a bar camp and we are Cool as Fuck!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Crappy Bar& {\color{purple} \faIcon{glass-martini-alt} }\end{tblr}\vspace{-1em}}

Come for a crappy drink. Leave because of the crappy jokes. But don't be hatin' on our crappy music 'cuz we just happy to be here...maybe.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Creature Comforts& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Uh-oh! Did you leave something small but mighty at camp??\n\nCreature Comforts is a cozy camp of seasoned burners offering the little things that make a big difference. From bandaids to earplugs, we've got you covered (we hope!). \n\nRooted in gifting and care, we try to help with the little things burners may have forgotten to keep you comfortable, grounded, and ready for the magic, day and night.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Cult of Pawpaw& {\color{purple} \faUserAstronaut \faMusic }\end{tblr}\vspace{-1em}}

The largest native fruit in the USA. We rejoice him



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}DPW (Dept of Public Works)& {\color{purple} }\end{tblr}\vspace{-1em}}

Dept of Public Works (DPW)



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}DreamCamp& {\color{purple} \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Come join us for mellow relaxation and connective nurturing.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Effigy Burn Field& {\color{purple} }\end{tblr}\vspace{-1em}}

Effigy Burn begins @ shortly after dusk  on Saturday



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}EleMENTAL& {\color{purple} \faChild \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Home of the Breakfast Bitches. Bevvy Bitches by night. Crafty Bitches welcome.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Emergency Weather - Grotto& {\color{purple} }\end{tblr}\vspace{-1em}}

Emergency Weather - Grotto



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Emergency Weather - North& {\color{purple} }\end{tblr}\vspace{-1em}}

Emergency Weather - North



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Emergency Weather - West& {\color{purple} }\end{tblr}\vspace{-1em}}

Emergency Weather - West



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}FAMILY'S FIRE PIT& {\color{purple} }\end{tblr}\vspace{-1em}}

FAMILY'S FIRE PIT does not have a description.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Fantasy Island& {\color{purple} \faUserAstronaut \faPizzaSlice \faMusic }\end{tblr}\vspace{-1em}}

Feeling adrift? Set sail for Fantasy Island and anchor yourself in good company, chill vibes, and alluring atmosphere, or splash around in our cool tunes. Fantasy Island, we'll be wading...



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Flow As You Go& {\color{purple} \faChild \faPalette \faMusic }\end{tblr}\vspace{-1em}}

Daytime shaded flowzone with pop-up classes and chill music on decks\nA cool down spot for hot hippies.  Spin things, dance, or just hang out.\nCome as you are, flow as you go.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Fuzzy Wuzzy& {\color{purple} \faIcon{glass-martini-alt} \faUmbrellaBeach \faMusic }\end{tblr}\vspace{-1em}}

Come join our psychedelic slumber party, to have all the fun with all your best friends you've always been wanting.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Galactic Printers& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Bring your spare clothes to us, and we'll jazz them up with our own blockprints! We'll have a variety of cosmic, hand-carved stamps and different ink colors to choose from.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Garden Party& {\color{purple} \faChild \faPizzaSlice \faMusic }\end{tblr}\vspace{-1em}}

A little bit of Alice in Wonderland. A little bit of Little Shop of Horrors. A lot of whimsy and magic! Garden Party is a celebration of plants, pastries, people and participation! Join us for tea parties and merry making. Weary travelers welcome!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Georgia Peanuts& {\color{purple} \faPizzaSlice }\end{tblr}\vspace{-1em}}

Wikipedia says, boiled peanuts are widely consumed and available in an area of the Southern United States. That describes us exactly. Guests are welcome to enjoy a cup full of boiled, salty nuts. (Food Allergy Warning: May contain peanut products.). If you are needing a different kind of help, our favorite peanut, Lucy, will be offering psychiatric assistance at her booth.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Go Outside Nerd& {\color{purple} }\end{tblr}\vspace{-1em}}

We don't have time for worthless chime-ins. Grab a foam weapon and start swinging.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Greeters& {\color{purple} }\end{tblr}\vspace{-1em}}

Greeters



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Grotto - Open Community Space& {\color{purple} }\end{tblr}\vspace{-1em}}

Shared community space \\& art zone and weather evacuation area\n\nThe Grotto is our vibrant communal event space where the spirit of Burning Man's principles come alive!\nImmerse yourself in the magic of spontaneous drumming circles, acoustic instrument jam sessions, and joyful celebrations, including weddings and games. The Grotto is a haven for creativity and connection, inviting you to embrace the principle of Immediacy. The Grotto is a grassy space nestled by impressive rock overhangs and capped by a delightful small waterfall.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Heart Mechanics& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Get Attune-UP at our interactive empathy practice installation to open your heart and then draw or write what you find there on the Heart Car.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Heathen Life& {\color{purple} \faUserAstronaut \faIcon{glass-martini-alt} \faMusic }\end{tblr}\vspace{-1em}}

Your variably friendly neighborhood Heathens return. \nBigger, badder, louder and prouder, and more orange, than before. Come celebrate a return to one of our favorite burns with us. Seek respite from the blistering summer sun and cool down with a crafted cocktail, enjoy our easy listening lounge, and say hey to the neighbors while you're here!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Horrible Trip Sitters& {\color{purple} \faIcon{glass-martini-alt} \faMusic }\end{tblr}\vspace{-1em}}

Total melting zone this is where you come to melt and vibe - adult drinks glow toys and UV area with body paint. Poi area and space to relax and melt and plenty of music. Plus extra madness from special guests



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Hydration Hoes& {\color{purple} }\end{tblr}\vspace{-1em}}

Come get your throat wet 💦



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Jenuine Love& {\color{purple} }\end{tblr}\vspace{-1em}}

I feel certain that Jenuine Love, the theme camp, has an amazing description, however, it has not been loaded into the Dust app.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Jungle of Obscurities& {\color{purple} }\end{tblr}\vspace{-1em}}

Looking for the rainbow mailboxes? Come here!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Just People& {\color{purple} \faUserAstronaut \faIcon{glass-martini-alt} \faMusic }\end{tblr}\vspace{-1em}}

Is it fun? If it is, we do it. If it's not, we cover it in liquor and do it anyway.\n\nAlso home of the Unprinciples and Every Burn Carry. Vote for your favorite truisms while you figure out what to do with your hands.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Kamp Khaos& {\color{purple} \faDice \faMusic }\end{tblr}\vspace{-1em}}

Hello there! Kamp Khaos is here! We have landed upon this realm to bring you a sight beyond sanity! A fun filled family friendly place to drag your siblings, friends, or whomever and beat them in the face! We are a fully immersive combat-oriented gladiator event just itching for you to take the first step unto GLORY!!

    Do you have what it takes to claw your way to the top? Can you, the wandering hipster, crush the competition and proclaim yourself the absolute winner!?! Do you have it in you to take on grandma and her flying dentures of doom? Can you survive the humiliation of that walker grinding your bones to dust as you lie defeated and broken on the floor? WHO KNOWS?! Come let us find out in the realms of Kamp Khaos where everyone wins!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Kamp Khaos Arena& {\color{purple} }\end{tblr}\vspace{-1em}}

Hello there! Kamp Khaos is here! We have landed upon this realm to bring you a sight beyond sanity! A fun filled family friendly place to drag your siblings, friends, or whomever and beat them in the face! We are a fully immersive combat-oriented gladiator event just itching for you to take the first step unto GLORY!!\n    Do you have what it takes to claw your way to the top? Can you, the wandering hipster, crush the competition and proclaim yourself the absolute winner!?! Do you have it in you to take on grandma and her flying dentures of doom? Can you survive the humiliation of that walker grinding your bones to dust as you lie defeated and broken on the floor? WHO KNOWS?! Come let us find out in the realms of Kamp Khaos where everyone wins!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Kamp Khaos Support Camp& {\color{purple} }\end{tblr}\vspace{-1em}}

Hello there! Kamp Khaos is here! We have landed upon this realm to bring you a sight beyond sanity! A fun filled family friendly place to drag your siblings, friends, or whomever and beat them in the face! We are a fully immersive combat-oriented gladiator event just itching for you to take the first step unto GLORY!!\n    Do you have what it takes to claw your way to the top? Can you, the wandering hipster, crush the competition and proclaim yourself the absolute winner!?! Do you have it in you to take on grandma and her flying dentures of doom? Can you survive the humiliation of that walker grinding your bones to dust as you lie defeated and broken on the floor? WHO KNOWS?! Come let us find out in the realms of Kamp Khaos where everyone wins!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Karaokemp!& {\color{purple} \faChild \faMusic }\end{tblr}\vspace{-1em}}

Live music day and night - performed by you!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}LAKE GUARDIANS& {\color{purple} }\end{tblr}\vspace{-1em}}

LAKE GUARDIANS are entrusted with the time-honored duties and responsibilities of reminding wayward burners that the waters of Luna Lake shall not be disturbed, nay even gazed upon, during endarkened hours. Betray not their guidance, for thou shalt exit the Moon forthwith and anon.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}LMK Enlightment - Art Support Team& {\color{purple} \faChild \faMusic }\end{tblr}\vspace{-1em}}

We are to support the LMK (Light, Music and Knowledge) Enlightment Art Project.\n\nWe will provide DJ capabilities and a variety of Live Music options as well as a whole program of LMK Audio/Visual Presets.  Don't miss our exclusive VIP Parties!!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}LSD (Leadership Support Division)& {\color{purple} }\end{tblr}\vspace{-1em}}

LSD (Leadership Support Division)



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Liminal& {\color{purple} \faPalette \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

A gallery of fabric art providing glimpses into realms of wondrous fungus.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Little Bohemia House Party& {\color{purple} \faMusic }\end{tblr}\vspace{-1em}}

L.B. House Party. Bring your snacks, bring your drink, bring your dance! Connect with friends and shake your booty.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Lunar Lake& {\color{purple} }\end{tblr}\vspace{-1em}}

Daytime only



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Medical⚕️& {\color{purple} }\end{tblr}\vspace{-1em}}

Medical



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Mission Control, Art, DMV& {\color{purple} }\end{tblr}\vspace{-1em}}

Mission Control: This is a place for people to come get information about burn happenings, times, locations, and whereabouts to things such as: workshops, theme camps, and events. Sometimes we even help people find themselves!\nArt: The Art Department stays connected with artists from initial inquiry to placement. \nDMV: Department of Mutant Vehicles



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Mythalia& {\color{purple} \faChild \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

A land of myth and legend where stories come to life.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Nudie Misfits& {\color{purple} \faUserAstronaut \faIcon{glass-martini-alt} }\end{tblr}\vspace{-1em}}

Nudie Misfits is a clothing-optional non-sexualized nudist lounge for the loud and irreverent. Join us daily for Naked Cocktail Hour and Friday for Naked Charcuterie!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}OVERFLOW Quiet Open Camping& {\color{purple} }\end{tblr}\vspace{-1em}}

OVERFLOW Quiet Open Camping does not have a description.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Open Camping& {\color{purple} }\end{tblr}\vspace{-1em}}

Open Camping does not have a description.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Open Camping \& RV/Car Camping& {\color{purple} }\end{tblr}\vspace{-1em}}

Open Camping \\& RV/Car Camping does not have a description.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Open Camping (Tents Only) NO MOTOR VEHICLES!& {\color{purple} }\end{tblr}\vspace{-1em}}

You MAY experience some levels of amplified sound throughout the day and night.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Parking& {\color{purple} }\end{tblr}\vspace{-1em}}

Parking



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Patchwork Petal Parlor& {\color{purple} \faChild \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Wander into camp through the colorful pathways of The Lady Garden, our solar garden that's beautiful by the sun and transformative by the moon. Come inside the Patchwork Parlor and sit a spell in our cozy lounge. Visit our origami station to find a peaceful moment of creative Regenesis.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Ponder& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

think about touching our orb



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Psilocybe Garden& {\color{purple} \faIcon{glass-martini-alt} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Step within this fairy ring and feel yourself become hypnotized by neon mycelium reaching up to 9FT, beckoning to come lay within, tempting you with trinkets, treats, and fancies of all kinds.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Quietish Open Camping (Tents Only)& {\color{purple} }\end{tblr}\vspace{-1em}}

Shhhhhh!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}RV Camping& {\color{purple} }\end{tblr}\vspace{-1em}}

(default friday rv parking)\r\nany rv arriving after thursday will be parked here



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Ranger HQ& {\color{purple} }\end{tblr}\vspace{-1em}}

Ranger HQ



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Reconnect Camp& {\color{purple} \faChild \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

✨Reconnect is your place to relax, refresh, and recharge.\nA space to regulate, get grounded, take a seat, and hydrate. We're always open, and you're always welcome.\n\nNestled close to the energy of our beautiful sound camps, Reconnect offers calming vibes without pulling you away from the action. Cool down, catch your breath, refill your canteen at our water station, and settle into our ample seating before heading back out to enjoy the experience.\n\nWe're here to help you reset so you can keep going strong.\n\nCome by, take a moment, and reconnect.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Renegade Sound& {\color{purple} \faMusic }\end{tblr}\vspace{-1em}}

Pop music all day and into the night



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}SILENT AND SHADY OPEN CAMPING TENTS ONLY NO GAS/DIESEL GENERATORS& {\color{purple} }\end{tblr}\vspace{-1em}}

SILENT AND SHADY OPEN CAMPING TENTS ONLY NO GAS/DIESEL GENERATORS does not have a description.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sacred Snack Shack& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Sacred Snack Shack is a playful sanctuary for seekers, mystics, deep feelers and curious wanderers drawn to connection and inner exploration. Whether you're decompressing, sharing late-night revelations, laughing with strangers-turned-friends or simply vibing in good company, this is a space to land exactly as you are. Come by and see what unfolds!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sacred Swarm& {\color{purple} }\end{tblr}\vspace{-1em}}

Sacred Swarm is an immersive hive-inspired playground centered around a glowing 32-foot geodesic dome transformed into a surreal adult jungle gym for the senses. Inspired by the communal intelligence and matriarchal structure of a beehive, the dome becomes a living swarm of movement, spectacle, and collective energy, as ``worker bees'' swing, lounge, and buzz through this space designed for exploration, connection, play, and wonder.\n\nComplementing the playground is a communal altar honoring personal icons, ancestors, artists, and visionaries who inspire us. Participants are invited to contribute offerings and symbols celebrating the divinity within ourselves and the people who shape our lives.\n\nPart sacred sanctuary, part cosmic circus, Sacred Swarm invites you to rest, play, connect, and lose yourself in the hum of the hive.\n\n(Brought to you by Camp MEOWee WOWee)



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sanctuary& {\color{purple} }\end{tblr}\vspace{-1em}}

Sanctuary



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sandtasia& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Like sands through the hourglass, so are the days of our lives.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sensua& {\color{purple} \faUserAstronaut \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

All things sensual



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sensua (Adults only)& {\color{purple} }\end{tblr}\vspace{-1em}}

All things sensual



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sound Central Open Camping (TENTS ONLY) NO MOTOR VEHICLES!& {\color{purple} }\end{tblr}\vspace{-1em}}

Amplified Sound will be surrounding this area. Do not camp here if you wish to not be near sound.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Space Clowns from Outer Space (IN YO SPACE!)& {\color{purple} \faMusic }\end{tblr}\vspace{-1em}}

A very completely well adjusted Clown brigade... weird



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Spectral Subverse& {\color{purple} \faIcon{glass-martini-alt} \faMusic }\end{tblr}\vspace{-1em}}

Welcome to a dimension where fire and photons collide! Our spectral stage will entrance the eye and ear, while our fire circle harbors the flame of performance all night long! Our LED dome is the perfect shaded getaway during those hot, sunny days, and blossoms into a web of colors at night. Come dance the night away and get lost in the maelstrom of the Subverse!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Starlit Sanctuary& {\color{purple} \faChild \faPizzaSlice \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

A celestial haven for explorers of presence, connection, and curiosity. Step into a space alive with light, color, and play; where community thrives, creativity flows, and every moment invites wonder. Whether under the sun or stars, find a place to rest, recharge, and revel in the magic of being fully alive.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Sunshine Yoga Cafe& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Looking for a soft place to land? Sunshine Yoga Cafe is your home-away-from-home for all things wellness. Come for our cafe, and stay for our daily yoga, meditation, and breathwork sessions. Get into the flow with us!\n\nBring your yoga mat, eye pillow, and your liquid vessel.\n\nAll times are subject to change with the weather, check the whiteboard for schedule updates.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Swag n Dab& {\color{purple} \faChild \faIcon{glass-martini-alt} \faUmbrellaBeach \faMusic }\end{tblr}\vspace{-1em}}

A lounge with multiple artists



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Tall Waterfall& {\color{purple} }\end{tblr}\vspace{-1em}}

Do not go past the waterfall!!!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Temple& {\color{purple} }\end{tblr}\vspace{-1em}}

Temple Art burn begins shortly after dusk Sunday night



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Temple of The Tea Monks& {\color{purple} \faPizzaSlice \faMusic }\end{tblr}\vspace{-1em}}

The Temple of the Tea Monks is an inclusive gathering space for all sentient beings including humans, robots, and crickets. A tea monk's brew is made using the finest teas, herbs and flowers. People come to the tent with their problems and leave with a lighter heart and a fresh brewed cup.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The BlackLit Moon& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Step out of the chaos and into the glow.\nBlack Lit Moon is a sanctuary for the senses, a late-night lounge where ultraviolet light transforms everything into something a little more magical. Dripping in neon art, soft textures, and slow energy, this camp is built for decompression, connection, and quiet awe. \nSink into soft seating, let the black lights paint your skin in color, and breathe. Whether you're coming down from the night, escaping the heat, or just craving a softer frequency, this is your place to land.\nExpect ambient soundscapes, glowing installations, and a rotating canvas of bodies and art illuminated in electric hues. No pressure. No performance. Just presence.\nFind the moon. Follow the glow. Stay as long as you need.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The Broken Drum& {\color{purple} \faChild \faIcon{glass-martini-alt} \faMusic }\end{tblr}\vspace{-1em}}

Yir favourite pub is back again! Bring your beleaguered wizzard butts for a sit and a drink (NA options available!). Trade in last year's robes for new frippery at the Damsel in dis dress.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The French Quarter& {\color{purple} \faPizzaSlice }\end{tblr}\vspace{-1em}}

Bonjour! Come visit us to relax and taste some cheeses, bread and wines you may have not tried before. We are also offering rope tastings, so you can experience wearing a rope harness, or just watching others get decorated with rope. Come visit the French Quarter



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The Green Room& {\color{purple} \faUmbrellaBeach \faMusic }\end{tblr}\vspace{-1em}}

The Green Room is a soft, verdant anomaly in the lunar landscape. Step into the limelight, stay for a song. The stage is yours. Just don't deepthroat the mics.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The Parlour& {\color{purple} \faUserAstronaut }\end{tblr}\vspace{-1em}}

An all inclusive, safe space to come explore your feral side in a intimate eclectic dungeon atmosphere



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The Surreal Saloon& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Wet your whistle at the Surreal Saloon! Saspirilla, face, body \\& nail support to get you READY for the burn \\& to reset/recharge afterwards. Relax and get WEIRD with us! Self-care has never been so surreal.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The Thirsty Frog Tavern& {\color{purple} \faUserAstronaut \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Conditioned air and good vibes



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The Thrifty Pickle& {\color{purple} }\end{tblr}\vspace{-1em}}

Are you thirsty? Is your wardrobe in need of a regensis? Let your rebirth begin at The Thrifty Pickle. Our bar meets free store will have you and your new self covered with fresh accessories, wearables for all sizes, and a variety of other novel treasures. If you're tired of your old vestments, you can leave them behind for the next pickler or save them for a rainy day.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}The whimsy Van winkle store& {\color{purple} \faUserAstronaut \faChild \faMusic }\end{tblr}\vspace{-1em}}

Camp Whimsy Van Winkle is a playful, immersive pop-up and lounge space offering a rotating collection of funky fashion, accessories, and adornments within a gifting-based experience. Come explore, get styled, and recharge in a cozy, whimsical environment.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Timey Wimey& {\color{purple} \faPizzaSlice \faDice }\end{tblr}\vspace{-1em}}

Timey wimey is the place you find on your late night wander! Swing by at night to chill by the fire and talk or come by during the day and play some games.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Toys, Treats, and Tiny Things& {\color{purple} \faChild \faPizzaSlice \faDice }\end{tblr}\vspace{-1em}}

We have assorted toys for all ages to play with, Pepper's miniature forms of art, and Stabby's mobile macaroon stand that will be there at burn:30. Come play! We also are home to a hole for the Mooney Putt Portal, it's a very tiny hole so look hard for it.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Tranquilitea& {\color{purple} \faUmbrellaBeach }\end{tblr}\vspace{-1em}}

Tea and a Safe Space



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Victory Surreal (art support for Kozyrev Echo \& Fire Cups)& {\color{purple} }\end{tblr}\vspace{-1em}}

We are an art support camp for the Kozyrev Echo and Fire Cups art installations



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Victory Surreal (art support for Kozyrev Echo)& {\color{purple} \faPalette }\end{tblr}\vspace{-1em}}

We are an art support camp for the Kozyrev Echo and Fire Cups art installations



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Viva San Escobar!& {\color{purple} \faChild \faMusic }\end{tblr}\vspace{-1em}}

San Escobar... not just a destination but also a state of mind.... Viva!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Wasted Potential& {\color{purple} \faChild \faUmbrellaBeach \faMusic }\end{tblr}\vspace{-1em}}

Make your everyday trash into extraordinary art by day and check out our DJ sound creations by night.  Campers explore creativity through sustainable sculpting, painting and designing one-of-a-kind art pieces.  Wasted Potential continues the party into the night with music, ambient electronic quantum sound bath medicine and a live DJ!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Wayward Bud& {\color{purple} \faPizzaSlice }\end{tblr}\vspace{-1em}}

Wayward Bud is a cozy, come as you are camp full of warmth, weirdness, and good company. Drift in, enjoy art made by campers, build a bowl at our late-night ramen bar, and stay a while for a delightfully wayward vibe.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}Wood Petter's Lounge& {\color{purple} \faIcon{glass-martini-alt} \faMusic }\end{tblr}\vspace{-1em}}

Lounge/Bar Area with Cool Wood Art, Dope Beats, Fire, and maybe a drink for you.



}



\vbox{

\subsection*{\begin{tblr}{Q[0.6\columnwidth]X[halign=r, valign=t]}World Spirits& {\color{purple} \faIcon{glass-martini-alt} }\end{tblr}\vspace{-1em}}

World Spirits is more than a bar. It's a chance to taste the world! Each year we raise a glass to a handful of countries with their most beloved (or infamous) liquor and share the story of its origin. What's more, we gamify the experience so that you can be involved, surprised and delighted!



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}camp gay& {\color{purple} \faUserAstronaut \faUmbrellaBeach \faMusic }\end{tblr}\vspace{-1em}}

if you enter this camp, ur gay <3 xo



}



\vbox{

\subsection*{\begin{tblr}{Q[0.7\columnwidth]X[halign=r, valign=t]}fablous hobo kamp& {\color{purple} }\end{tblr}\vspace{-1em}}

Hobo arts and things



}



